2019 Draft Prep

### 2019-03-23 draftPrep.Rmd
Still working on the tiers and approach

---
title: "2019 Draft Prep"
author: "Tom Kain"
date: "March 19, 2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

@@

*Note, one of the excluded keepers is mine - SS Trevor Story, round 11*

@@

```{r echo = FALSE}
positions_ranked_with_keepers %>%
  filter(z_sum >= 15) %>%
  select(Name, z_sum, ADP, round) %>%
  unique() %>%
  arrange(ADP) %>%
  kable()
```

@@

>>>>

---
title: "2019 Draft Prep"
author: "Tom Kain"
date: "March 19, 2019"
output:
  html_document:
    df_print: paged
  pdf_document: default
editor_options:
  chunk_output_type: console
---

@@

```{r echo=FALSE}
positions_ranked_with_keepers %>%
  filter(!keeper,
         ADP <=300) %>%
  arrange(round, position) %>%
  mutate(round = as_factor(round)) %>%
  mutate(round = fct_inseq(round, ordered = TRUE)) %>%
  ggplot(aes(x=round,y=z_sum,alpha=desc(z_rank),size=z_sum,color=position)) +
  geom_jitter(aes(text=Name)) +
  facet_wrap(~ position) -> rv

ggplotly(rv)
```
*Note, one of the excluded keepers is mine - SS Trevor Story, round 11*

@@

```{r echo = FALSE}
positions_ranked_with_keepers %>%
  filter(z_sum >= 15, !keeper) %>%
  select(Name, z_sum, ADP, round) %>%
  unique() %>%
  arrange(ADP) %>%
  kable()
```

@@

##### Damn Good Tier (z_score between 10 and 15)

```{r echo = FALSE}
positions_ranked_with_keepers %>%
  filter(between(z_sum,10,15), !keeper) %>%
  ggplot(aes(position,z_sum,size=round,color=Name)) +
  geom_jitter(aes(text=Name), width = .2) -> dgt

ggplotly(dgt)

positions_ranked_with_keepers %>%
  filter(between(z_sum,10,15), !keeper) %>%
  count(position) %>%
  arrange(desc(n)) %>%
  kable()
```

At the top of this tier are two first basemen (Votto, Rizzo) and two outfielders (Yelich, Martinez). Votto has been going late enough (round 6) that I can afford to wait, giving me some fallback options in the OF if Harper and Soto are not available first. Although Bregman and Judge are next up, I'm thinking Jose Altuve might be a good pick since 2B is relatively scarce compared to OF and 3B.

##### Pretty Good Tier

```{r echo=FALSE}
positions_ranked_with_keepers %>%
  filter(between(z_sum,5,10), !keeper) %>%
  ggplot(aes(position,z_sum,size=round,color=Name)) +
  geom_jitter(aes(text=Name), width = .2) -> dgt

ggplotly(dgt)

positions_ranked_with_keepers %>%
  filter(between(z_sum,5,10), !keeper) %>%
  count(position) %>%
  arrange(desc(n)) %>%
  kable()
```
